Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-08 paper/paper.tex
w->d

For classification we use the {\tt creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
\begin{align*}
p(y& \mid \textbf{w}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{w}, i) ,
\end{align*}
where $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}

>>>>

For classification we use the {\tt creg} regression modeling framework to train a 11-class logistic regression classifier.\footnote{https://github.com/redpony/creg}  We parameterize the L1 classifier as a multiclass logistic regression:
\begin{align*}
p(y& \mid \textbf{d}, i) \propto \exp \sum_j \lambda_j h_j(y, \textbf{d}, i) ,
\end{align*}
where $\textbf{d}$ are documents, $h_j(\cdot)$ are feature functions, $\lambda_j$ are the corresponding weights, and $y$ refer to the outputs: eleven L1 class labels. \yt{regularization???}
